\documentclass[12pt]{article}

\usepackage{graphicx}
\usepackage{paralist}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{hhline}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{multicol}

\oddsidemargin 0mm
\evensidemargin 0mm
\textwidth 160mm
\textheight 200mm
\renewcommand\baselinestretch{1.0}
\usepackage[normalem]{ulem}

\pagestyle {plain}
\pagenumbering{arabic}

\newcounter{stepnum}

\usepackage{color}

\title{SE3XA3 Group 6 Problem Statement}
\author{Mohammad Hussain, hussam17, 400081369\\
		\and 
		Brian Jonatan, jonatans, 400072396
		\and
		Shivaansh Prasann, prasanns, 400100351}

\begin {document}

\maketitle

Consider a software engineer trying to develop a zombie survival game {\color{magenta} for a target audience of 15-25 year olds who will play it in a home setting on a desktop computer or laptop}.
The initial process of making each individual feature such as a playable \sout{map} {\color{magenta} terrain}, 
moveable character, combat system, inventory system, and 
enemy AI are all very time consuming. However, if a good basic foundation that 
covers all the basic features stated existed, the developer could focus more on 
creating their unique vision for the game starting from the foundation given. {\color{magenta} Group 6ix will create a zombie survival
development kit, with all of the aforementioned features implemented. This allows aspiring game developers to easily get started on what they want
to make specific to the game, rather than worrying about developing the complicated foundation. New developers will add things that are already not implemented
in the dev kit; features such as menu screens, a plotline, NPCs, or a scoring system. Stakeholders involved in this project include Group 6ix, testers, and the instructor/TAs
of SFWR 3XA3, as these groups are responsible for the making and verification of the development kit. The customers are aspiring game developers who want to skip implementing
the base features of a game. Other stakeholders include the users of the games created by programmers who use this dev kit, as their game only exists due to Group 6ix's creation. }


\sout{All the aforementioned features are the works given in the open source project, Zombie Survival Kit.
Group 6 will use this foundation and rework it from the ground up to make a fully fledged, playable 
zombie survival game rather than just individual features put together in a Unity project.}

\end {document}